---
title: "Syllabus"
output:
  html_document:
    df_print: paged
---

## About the Course {#about-the-course .smith}

#### Instructor

-   Scott LaCombe (`slacombe@smith.edu`).Wright Hall 201. My hours will be held on Mondays from 2-3 PM, Wednesdays from 11-12, and Thursdays from 4:15-5:15 PM. Mondays and Wednesdays are by appointment slots and hybrid ([sign up here](https://calendar.google.com/calendar/u/0/selfsched?sstoken=UUVsekFOdmJUYzVyfGRlZmF1bHR8MGY0NWUyMWJlMTk3M2ExMzc4YTdmMzM1NGI0MDY5Zjc)), and Thursdays are in person and open.

#### Description and Goals



#### Readings

#### Class Structure


## Policies {#policies .unnumbered}

#### Attendance

Participation has two components: 1) being present and 2) engaging in class activities. Your participation is an important part of the process of learning statistics, and we need you in class to help stimulate discussion. You can make a valuable contribution to the discussion by bringing up connections between our work and study designs you have seen in other courses, in the newspaper, or in research literature. I realize that, especially during these difficult times, you won't always be able to get to class. If you miss class, I ask that you make up for your participation by posting something on slack such as a question about course material, article that relates to course content, or anything else related to course content. I will record lectures and post them on Moodle, but the classroom will not be hybrid. The recording may not pick up everything we cover in class so I encourage you to attend in person. You get one free absence where you do not need to make up for lost participation.

#### Collaboration

Much of this course will operate on a collaborative basis, and you are expected and encouraged to work together with a partner or in small groups to study, complete homework assignments, and prepare for exams. However, **every word that you write must be your own unless I'm explicitly asking you to submit a group submission**. Copying and pasting sentences, paragraphs, or blocks of code from another student is not acceptable and will receive no credit. No interaction with anyone but the instructor and course assistant is allowed on any exams. All students, staff and faculty are bound by the Smith College Honor Code.

#### Academic Honor Code Statement

Cases of dishonesty, plagiarism, or other infractions, will be reported to the Academic Honor Board. You must always provide appropriate citations for others' work and ideas. Giving other scholars due credit in your written and oral communication is a fundamental social gesture in academic work---a way for us to acknowledge each other's scholarship and signify that we respect each other.

From the [Smith honor code website](https://www.smith.edu/sao/handbook/socialconduct/honorcode.php):

> Smith College expects all students to be honest and committed to the principles of academic and intellectual integrity in their preparation and submission of course work and examinations. Students and faculty at Smith are part of an academic community defined by its commitment to scholarship, which depends on scrupulous and attentive acknowledgement of all sources of information, and honest and respectful use of college resources. **Cases of dishonesty, plagiarism, etc., will be reported to the Academic Honor Board.**

#### Classroom Environment

#### Accommodations

Everyone should have all that they need to succeed in this course. Please send me your accommodation letter, or have the Disability Office work with me. If you need to register for accommodations, please contact the Disability Services office at ODS\@smith.edu. Please check out the office [website](https://www.smith.edu/ods/) for more information. Smith provides flexible and individualized accommodation to students with documented disabilities that may affect their ability to fully participate in course activities or to meet course requirements. To receive accommodation services, students must be registered with the Smith College Disability Services office, College Hall 104; phone: (413) 585-2071 (voice, TTY, TDD). Students with disabilities are encouraged to contact the instructor for a confidential discussion of their individual needs for academic accommodation.

If you have special needs concerning quiz taking, please bring documentation of your needs and make an appointment to discuss them with me, at least ONE WEEK BEFORE the first exxam. That will give me time to provide accommodation for your needs.

## Assignments {#assignments .unnumbered}

 instructions for the projects will be posted on the course website.

#### Summary

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
Assignment <- c("Homework", "Participation", "Exams", 
                "Mini Project 1", "Mini Project 2", "Final Grade")
`Percent of Total` <- c("40%", "10%", "20%", "10%", "20%", "100%")
`Due Date` <- c("Fridays", "Daily", "March 9th and April 27th", "March 24", "May 12", "")
kable(cbind(Assignment, `Percent of Total`, `Due Date`))
```

#### Grading

When I grade your written work, I am looking for problem solutions that are technically correct and reasoning that is clearly explained. Numerically correct answers, alone, are not sufficient on homework or exams. I value neatness and brief, clear, well-organized answers that explain your thinking. If the grader cannot read or follow your work, they cannot give you credit for it. The grader will check each homework submission for completeness and grade a subset of the exercises. Homework answer keys will be posted on Moodle after the due date.

#### Assignment Late Policy

For every day late on the written assignments I will reduce your grade for that assignment by ten percent. I will not accept any late final group research reports.

#### Final Grade Brackets

```{r, echo=FALSE}
Grade <- c("A", "A-", "B+", "B", "B-", "C+", "C", "C-", "D+", "D", "E")
Percent <- c("95-100%", "90-95%", "87-89%",	"83-86%",	"80-82%", "77-79%", "73-76%", "70-72%", "60-66%", "67-69%", "59% and below")
kable(cbind(Grade, Percent))
```

## Resources {#resources .unnumbered}

#### Course Website and Moodle

The [course website](https://lacombe129.github.io/SDS290/) will be regularly updated with lecture slides, project information, assignments, and other course resources. Assignments and grades will be submitted via Moodle. You should check both regularly.

#### Computing

The use of the `R` statistical computing environment with the [RStudio](http://rstudio.org) interface is thoroughly integrated into the course. You have two options for using `RStudio`:

-   The **server** version of `RStudio` on the [web](http://rstudio.smith.edu). The advantage of using the server version is that all of your work will be stored in the cloud, where it is automatically saved and backed up. This means that you can access your work from any computer with a web browser (Firefox is recommended) and an Internet connection.
-   A **desktop** version of `RStudio` installed on your machine. The downside to this approach is that your work is only stored locally, and you will have to manage your own installation. Nevertheless, I still recommend this option because you do not need wifi or network access to work, and you know it is on your computer. I find collaboration easier with this method too.

Note that you do not have to choose one or the other -- you may use both. However, it is important that you understand the distinction so that you can keep track of your work. Both `R` and `RStudio` are free and open-source, and are installed on most computer labs on campus. Please see the [Resources](resources.html) page for help with `R`.

#### Use of Technology during Class

As we will always be using our computers to attend this course, I hope it goes without saying that while the class is in session, you should resist the temptation to use your computer or cell phone for personal email, web browsing, social media, or any activity that's not related to the class.

#### Writing

Your ability to communicate results, which may be technical in nature, to your audience, which is likely to be non-technical, is critical to your success as a data analyst. The assignments in this class will place an emphasis on the clarity of your writing.

#### Extra Help

There are [Statistics TAs](https://www.smith.edu/qlc/tutoring.html?colStats=open#PanelStats) available from 7:00-9:00pm on Sunday--Thursday evenings in Sabin-Reed 301. In addition, the Spinelli Center for Quantitative Learning (Seeley 207) supports students doing quantitative work across the curriculum. Your fellow students are also an excellent source for explanations, tips, etc.

#### Tentative Schedule

Please refer to the complete [day-to-day schedule](https://docs.google.com/spreadsheets/d/1VIHs_2swDFnkW2ZLJWqQ4sh8SRVGZFgmJg8ukphfIVs/edit?usp=sharing) for more detailed information.
